HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
rephrased DA, stressing the issue with getting annotations

Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate translation on a fine-grained scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores, that correlate very strongly with one other.

We followed~\parcite{graham2015accurate} and collected 10 adequacy
judgements on most of the HUME annotated translations for
German and Romanian, using the CrowdFlower platform\footnote{\url{https://www.crowdflower.com}}. To ensure high quality judgments we restricted the IP of the annotators to those of the relevant country. Czech and Polish judgements were
excluded, as our experiments only yielded very little high quality data.

>>>>

Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting accuracy ratings, direct assessment (DA).
%By crowdsourcing a large number of adequacy judgements for each candidate translation on a fine-grained scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores, that correlate very strongly with one other.
Statistical interpretation of a large number of crowd-sourced adequacy
judgements for each candidate translation on a fine-grained scale of 0 to 100
results in reliable aggregate scores, that correlate very strongly with one
other.

We attempted to follow \perscite{graham2015accurate} but struggled to get enough
judgements for our target languages. We ended up with 10 adequacy 
judgements on most of the HUME annotated translations for
German and Romanian but insufficient data for Czech and Polish. We see this as a
severe practical limitation of DA.
%We followed~\parcite{graham2015accurate} and collected 10 adequacy
%judgements on most of the HUME annotated translations for
%German and Romanian, using the CrowdFlower platform\footnote{\url{https://www.crowdflower.com}}. To ensure high quality judgments we restricted the IP of the annotators to those of the relevant country. Czech and Polish judgements were
%excluded, as our experiments only yielded very little high quality data.
